Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-05-21 SecDev21/paper.tex

Ada and SPARK offer an easy-to-use mechanism for interfacing with C code \cite{}. The mechanism allows C-written function to be called by Ada/SPARK code and vice versa and for representing shared data objects. The memory representations of a shared data object must be the same in both the C and the SPARK code. For instance, if a C function is called with a 32-bits integer argument, the SPARK interface of this function should also be called with a 32-bits integer argument. It is the responsibility of the user to ensure this.

Although formal verification can only be applied to the SPARK translated code,  pre- and post-conditions can be attached to C functions interfaced in SPARK to allow reasoning about the side effects of calling these functions by the SPARK code. Since the functional specification of these contracts can not be proved, it is the programmer's role to ensure their correctness. Interfacing C and SPARK code can be error-prone if it is not done carefully. \Cref{sec:verif} discusses how to mitigate this issue effectively.

>>>>

Ada and SPARK offer an easy-to-use mechanism for interfacing with C code. The mechanism allows  C-written functions to be called by Ada/SPARK code and vice versa, via function bindings \cite{Ada_C_Binding}, and for the representation of shared data objects by the two languages. The memory representations of a shared data object must be the same in both the C and the SPARK code. For instance, if a C function is called with a 32-bits integer argument, the SPARK binding of this function should also be called with a 32-bits integer argument. It is the responsibility of the user to ensure this.

Although formal verification can only be applied to the SPARK translated code, pre- and post-conditions can be attached to C functions bindings in SPARK to allow the formal verification tools to reason about side effects of calling these functions that can affect the SPARK code. Since the functional specification of these contracts can not be proved, it is the programmer's role to ensure their correctness. Interfacing C and SPARK code can be error-prone if it is not done carefully. \Cref{sec:verif} discusses how to mitigate this issue effectively.
